---
title: "20190516_log_env_variables_GitHub"
author: "Nations"
date: "5/16/1019"
output: html_document
---
### This script estimates the effect of environmental variables on log-transformed body mass
This includes individual variables as well as interactions

Set working directory here
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/User.....")
```

Required packages
```{r, message=FALSE}
library(tidyverse)
library(phytools)
library(geiger)
library(brms)
getwd()
```
Reading in data.

#### Center scaling all of the variables to make the interaction models more interpretable
```{r}
tree <- read.tree("Pseudomys_Division_Tree.nwk")
tree <- drop.tip(tree, "Pseudomys_pedunculatus")
dat <- read.csv("Pseudomys_division_data.csv", header=TRUE,row.names=1, stringsAsFactors=FALSE)
dat$log_mass <-log(dat$mass)
dat$cmass <- dat$mass - mean(dat$mass)
dat$temp <- dat$l_temp - mean(dat$l_temp)
dat$ar <- dat$l_ar - mean(dat$l_ar)
dat$pam <- dat$l_pam - mean(dat$l_pam)
dat$el <- dat$l_el - mean(dat$l_el)
dat$pas <- dat$l_pas - mean(dat$l_pas)
dat$pwm <- dat$l_pwm - mean(dat$l_pwm)
dat$tar <- dat$l_tar - mean(dat$l_tar)
dat$npp <- dat$l_npp - mean(dat$l_npp)
dat$lat <- dat$latitude - mean(dat$latitude)
#data$st <- scale(data$Temperature_annual_mean)
```

phylo data
```{r}
inv.phylo <- MCMCglmm::inverseA(tree, nodes = "TIPS", scale = TRUE)
A <- solve(inv.phylo$Ainv)
rownames(A) <- rownames(inv.phylo$Ainv)
```

#### Linear regression with categorial dependent variables (habitat) and phylo
This is a single model for all the 7 non-correlated variables
This includes measurement error

####Temperature Annual Mean
```{r, message = FALSE}
g.tam <- brm(
  log_mass ~ 1 + me(temp, sdx = temp_lsd) + (1 + me(temp, sdx = temp_lsd)|group) + (1|phylo), 
  data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metempsdxEQtemp_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
  file = "20190426_log_tam.Rds"
)
#g.tam <- add_criterion(g.tam, criterion = c("loo", "waic", "kfold"), overwrite = T)
```


```{r}
summary(g.tam)
plot(g.tam, ask = F)
plot(marginal_effects(g.tam), points = T)
```

#### Precipitation Annual Mean
```{r, message = FALSE}
g.pam <- brm(
  log_mass ~ 1 + me(pam, pam_lsd) + (1 + me(pam, pam_lsd)|group) + (1|phylo), 
  #log_mass ~ 1 + me(precip, precip_lsd) + (1 + me(precip, precip_lsd)|group), 
  data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepampam_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
  file = "20190426_log_pam.Rds"
)
#g.pam <- add_criterion(g.pam, criterion = c("loo", "waic", "kfold"), overwrite = T)
```

```{r}
summary(g.pam)
plot(g.pam, ask = F)
plot(marginal_effects(g.pam), points = T)
```


#### elevation
```{r, message = FALSE}
g.el <- brm(
  log_mass ~ 1 + me(el, el_lsd) + (1 + me(el, el_lsd)|group) + (1|phylo), 
  data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "meelel_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
  file = "20190426_log_el.Rds"
)
#g.el <- add_criterion(g.el, criterion = c("loo", "waic", "kfold"), overwrite = T)
```

```{r}
summary(g.el)
plot(g.el, ask = F)
plot(marginal_effects(g.el), points = T)
```


#### Aridity Index
```{r, message = FALSE}
g.ar <- brm(
  log_mass ~ 1 + me(ar, ar_lsd) + (1 + me(ar, ar_lsd)|group) + (1|phylo), 
  #log_mass ~ 1 + me(aridity, aridity_lsd) + (1 + me(aridity, aridity_lsd)|group), 
  data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mearar_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
  file = "20190426_log_ar.Rds"
)
#g.ar <- add_criterion(g.ar, criterion = c("loo", "waic", "kfold"), overwrite = T)
```

```{r}
summary(g.ar)
plot(g.ar, ask = F)
plot(marginal_effects(g.ar), points = T)
```



####Precip Wettest Month
```{r, message = FALSE}
g.pwm <- brm(
  log_mass ~ 1 + me(pwm, pwm_lsd) + (1 + me(pwm, pwm_lsd)|group) + (1|phylo), 
  #log_mass ~ 1 + me(pwmidity, pwmidity_lsd) + (1 + me(pwmidity, pwmidity_lsd)|group), 
  data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepwmpwm_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
  file = "20190426_log_pwm.Rds"
)
#g.pwm <- add_criterion(g.pwm, criterion = c("loo", "waic", "kfold"), overwrite = T)
```


```{r}
summary(g.pwm)
plot(g.pwm, ask = F)
plot(marginal_effects(g.pwm), points = T)
```


####Temperature Annual Range
```{r, message = FALSE}
g.tar <- brm(
  log_mass ~ 1 + me(tar, tar_lsd) + (1 + me(tar, tar_lsd)|group) + (1|phylo), 
  #log_mass ~ 1 + me(tamidity, tamidity_lsd) + (1 + me(tamidity, tamidity_lsd)|group), 
  data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metartar_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
  file = "20190426_log_tar.Rds"
)
#g.tam <- add_criterion(g.tam, criterion = c("loo", "waic", "kfold"), overwrite = T)
```


```{r}
summary(g.tar)
plot(g.tar, ask = F)
plot(marginal_effects(g.tar), points = T)
```


####Precipitation Annual Seasonality Ratio
```{r, message = FALSE}
g.pas <- brm(
  log_mass ~ 1 + me(pas, pas_lsd) + (1 + me(pas, pas_lsd)|group) + (1|phylo), 
  #log_mass ~ 1 + me(pasidity, pasidity_lsd) + (1 + me(pasidity, pasidity_lsd)|group), 
  data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepaspas_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
  file = "20190426_log_pas.Rds"
)
#g.pas <- add_criterion(g.pas, criterion = c("loo", "waic", "kfold"), overwrite = T)
```


```{r}
summary(g.pas)
plot(g.pas, ask = F)
plot(marginal_effects(g.pas), points = T)
```

```{r, message = FALSE}
g.npp <- brm(
  log_mass ~ 1 + me(npp, npp_lsd) + (1 + me(npp, npp_lsd)|group) + (1|phylo), 
  #log_mass ~ 1 + me(pasidity, pasidity_lsd) + (1 + me(pasidity, pasidity_lsd)|group), 
  data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "menppnpp_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
  file = "20190426_log_npp.Rds"
)
#g.npp <- add_criterion(g.npp, criterion = c("loo", "waic", "kfold"), overwrite = T)
```

```{r}
summary(g.npp)
plot(g.npp, ask = F)
plot(marginal_effects(g.npp), points = T)
```

Gotta add in g.lat
```{r}
g.lat <- brm(
  log_mass ~ 1 + me(lat, lat_sd) + (1 + me(lat, lat_sd)|group) + (1|phylo), 
  #log_mass ~ 1 + me(pasidity, pasidity_lsd) + (1 + me(pasidity, pasidity_lsd)|group), 
  data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "melatlat_sd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
  file = "20190426_lat.Rds"
)
```

```{r}
summary(g.lat)
plot(g.lat, ask = F)
plot(marginal_effects(g.lat), points = T)
```

##Interactions
These are models of the interactions between two variables

####Precip Annual Mean and Temperature Annual Mean
```{r, message = FALSE}
i.pamtam <- brm(
 log_mass ~  me(pam, pam_lsd)*me(temp, temp_lsd) + (1 + me(pam, pam_lsd)*me(temp, temp_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepampam_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metemptemp_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
  file = "20190426_log_i_pamtam.Rds"
)
```

```{r}
summary(i.pamtam)
plot(i.pamtam, ask = F)
#plot(marginal_effects(i.pamtam, effects = "pam"), points = T)
#plot(marginal_effects(c.tam))
```


#### Precip Annual Mean and Precip Wettest Month
```{r, message = FALSE}
i.pampwm <- brm(
 log_mass ~  me(pam, pam_lsd)*me(pwm, pwm_lsd) + (1 + me(pam, pam_lsd)*me(pwm, pwm_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepampam_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepwmpwm_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_pampwm.Rds"
)
```



```{r}
summary(i.pampwm)
plot(i.pampwm, ask = F)
#plot(marginal_effects(i.pampwm, effects = "pam:pwm"), points = T)
#plot(marginal_effects(c.tam))
```


#### Precip Annual Mean and Temperature Annual Range
```{r, message = FALSE}
i.pamtar <- brm(
 log_mass ~  me(pam, pam_lsd)*me(tar, tar_lsd) + (1 + me(pam, pam_lsd)*me(tar, tar_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepampam_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metartar_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_pamtar.Rds"
)
```


```{r}
summary(i.pamtar)
plot(i.pamtar, ask = F)
#plot(marginal_effects(i.pamtar, effects = "pam:tar"), points = T)
#plot(marginal_effects(c.tam))
```



#### Precip Wettest Month and Temperature Annual Range
```{r, message = FALSE}
i.pwmtar <- brm(
 log_mass ~  me(pwm, pwm_lsd)*me(tar, tar_lsd) + (1 + me(pwm, pwm_lsd)*me(tar, tar_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepwmpwm_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metartar_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_pwmtar.Rds"
)
```


```{r}
summary(i.pwmtar)
plot(i.pwmtar, ask = F)
#plot(marginal_effects(i.pwmtar, effects = "pwm:tar"), points = T)
#plot(marginal_effects(c.tam))
```


#### Precip Wettest Month and Temp Annual Mean
```{r, message = FALSE}
i.pwmtam <- brm(
 log_mass ~  me(pwm, pwm_lsd)*me(temp, temp_lsd) + (1 + me(pwm, pwm_lsd)*me(temp, temp_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepwmpwm_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metemptemp_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_pwmtam.Rds"
)
```


```{r}
summary(i.pwmtam)
plot(i.pwmtam, ask = F)
#plot(marginal_effects(i.pwmtam, effects = "pwm:temp"), points = T)
#plot(marginal_effects(i.pwmtam))
```


#### Temperature Annual Range and Temperature Annual Mean
```{r, message = FALSE}
i.tartam <- brm(
 log_mass ~  me(tar, tar_lsd)*me(temp, temp_lsd) + (1 + me(tar, tar_lsd)*me(temp, temp_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metartar_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metemptemp_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_tartam.Rds"
)
```

```{r}
summary(i.tartam)
plot(i.tartam, ask = F)
#plot(marginal_effects(i.tartam, effects = "tar:temp"), points = T)
```


#### Net Primary Productivity and Temperature Annual Mean
```{r, message = FALSE}
i.npptam <- brm(
 log_mass ~  me(npp, npp_lsd)*me(temp, temp_lsd) + (1 + me(npp, npp_lsd)*me(temp, temp_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "menppnpp_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metemptemp_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_npptam.Rds"
)
```

```{r}
summary(i.npptam)
plot(i.npptam, ask = F)
#plot(marginal_effects(i.npptam, effects = "npp:temp"), points = T)
#plot(marginal_effects(c.tam))
```


#### Net Primary Productivity and Precip Annual Mean
```{r, message = FALSE}
i.npppam <- brm(
 log_mass ~  me(npp, npp_lsd)*me(pam, pam_lsd) + (1 + me(npp, npp_lsd)*me(pam, pam_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "menppnpp_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepampam_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_npppam.Rds"
)
```

```{r}
summary(i.npppam)
plot(i.npppam, ask = F)
#plot(marginal_effects(i.npppam, effects = "npp:pam"), points = T)
#plot(marginal_effects(c.tam))
```


####Aridity: Temp annual mean
```{r}
i.artam <- brm(
 log_mass ~  me(ar, ar_lsd)*me(temp, temp_lsd) + (1 + me(ar, ar_lsd)*me(temp, temp_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mearar_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metemptemp_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_artam.Rds"
)
```


```{r}
summary(i.artam)
plot(i.artam, ask = F)
#plot(marginal_effects(i.artam, effects = "ar:tam"), points = T)
```


#### Aridity : Precip Wettest Month
```{r}
i.arpwm <- brm(
 log_mass ~  me(ar, ar_lsd)*me(pwm, pwm_lsd) + (1 + me(ar, ar_lsd)*me(pwm, pwm_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mearar_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepwmpwm_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_arpwm.Rds"
)
```


```{r}
summary(i.arpwm)
plot(i.arpwm, ask = F)
#plot(marginal_effects(i.arpwm, effects = "ar:pwm"), points = T)
```



arnpp

#### Aridity : Net Primary Production
```{r}
i.arnpp <- brm(
 log_mass ~  me(ar, ar_lsd)*me(npp, npp_lsd) + (1 + me(ar, ar_lsd)*me(npp, npp_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mearar_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "menppnpp_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_arnpp.Rds"
)
```


```{r}
summary(i.arnpp)
plot(i.arnpp, ask = F)
#plot(marginal_effects(i.arnpp, effects = "ar:npp"), points = T)
```



#### Aridity : Precip Annual Mean
```{r}
i.arpam <- brm(
 log_mass ~  me(ar, ar_lsd)*me(pam, pam_lsd) + (1 + me(ar, ar_lsd)*me(pam, pam_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mearar_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mepampam_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_arpam.Rds"
)
```


```{r}
summary(i.arpam)
plot(i.arpam, ask = F)
#plot(marginal_effects(i.arpam, effects = "ar:pam"), points = T)
```


#### Aridity : Temp annual range

```{r}
i.artar <- brm(
 log_mass ~  me(ar, ar_lsd)*me(tar, tar_lsd) + (1 + me(ar, ar_lsd)*me(tar, tar_lsd)|group) + (1 | phylo), 
 data = dat, 
  family = gaussian(link = "identity"), cov_ranef = list(phylo = A),
  iter = 5000, 
prior = c(
   set_prior("normal(0,5)", class = "b"),
   set_prior("normal(0,5)", class = "Intercept"),
   set_prior("normal(0,5)", class = "sd", coef = "Intercept", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "mearar_lsd", group = "group"),
   set_prior("normal(0,5)", class = "sd", coef = "metartar_lsd", group = "group"),
   set_prior("student_t(3,0.5,20)", class = "sd", coef = "Intercept", group = "phylo"),
   set_prior("lkj(2)", class = "cor"),
   #set_prior("normal(0,5)", class = "sigma")),
   set_prior("chi_square(10)", class = "sigma")),
  save_mevars = T,
  control = list(adapt_delta = 0.99, max_treedepth = (15)),
  cores = parallel::detectCores(),
   file = "20190426_log_i_artar.Rds"
)
```


```{r}
summary(i.artar)
plot(i.artar, ask = F)
#plot(marginal_effects(i.artar, effects = "ar:tar"), points = T)
```
